Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
A.B. review: clarify runtime adv. of PCA vs filters

% - PCA shows similar performance but probably requires tuning of main components -> check runtime!
The PCA approach did neither show the best or worst result in the lineup.
It shines in terms of runtime since it reduces the amount of features highly.
However, it also removes the option for a post-analysis of feature importance by squashing predictors into principal components and users need to decided upfront what they value more.
Since filters are only calculated once due to caching, the runtime advantage might in fact be negligible in practice.

>>>>

% - PCA shows similar performance but probably requires tuning of main components -> check runtime!
The PCA approach did neither show the best or worst result when being compared to other feature-selection approaches.
It is able to reduce model fitting times substantially due to its nature of reducing the number of predictors to a minimum.
However, it also removes the possibility to conduct a post-analysis of feature importance by combining predictors into principal components, forcing users to decide upfront what they value more.
Since filter scores only need to be calculated once in a benchmark setting, the runtime advantage might in fact be negligible in practice.
